Learning constraints in spreadsheets and tabular data

### 2016-11-28 Paper/ECAI/tabular.tex
added a note on the noise handling

A final direction is that the current approach assumes noise-free data (but see the part on error correction); in inductive logic programming there has been much work on how to handle noisy data, while in constraint satisfaction a popular alternative is to consider \textit{soft} constraints that can be violated (at a cost). 
This could extend the approach to new application domains, beyond traditional spreadsheets.

>>>>

\added{A final direction is that the current approach assumes noise-free data (but see the part on error correction); in inductive logic programming there has been much work on how to handle noisy data such as allowing a tolerance level $\epsilon$ when a rule or a constraint $\sum_{i=1}^n b_i = c$ matches up to $\epsilon$: $|\sum_{i=1}^n b_i - c| \leq \epsilon$, while in constraint satisfaction a popular alternative is to consider \textit{soft} constraints that can be violated at a cost, which is a real value and then the task is to find top-$k$ best matching constraints. }
This could extend the approach to new application domains, beyond traditional spreadsheets.
